```latex
\documentclass[10pt]{resume-template} % Document class file. The '10pt' option selects 10-point font size; if you prefer 12pt, replace {}with {12pt}.

\usepackage{lmodern} % Uses the Latin Modern Font which scales nicely to different paper sizes.
\usepackage[english]{babel} % English language/hyphenation setup.

\input{user_logs/2024_08_25_14_29_17/2024_08_25_14_29_17.tex} % Include the user's data here.

\begin{document}

% Start of document body.
\section{\faUsers}{\Large User Information}
John Doe \hfill \faEnvelopeO(john.doe@email.com)
123 Tech Avenue, San Francisco, CA 94105 \hfill (555) 123-4567
\newline LinkedIn: linkedin.com/in/johndoe
\newline GitHub: github.com/johndoe

\section{\faPencilSolid}{\Large Professional Summary}
Highly skilled Software Engineer with over 3 years of experience in designing, developing, and maintaining web applications. Proven expertise in Python, JavaScript, React, and Node.js. Adept at collaborating with cross-functional teams to deliver high-quality software solutions. Strong background in problem-solving, agile methodologies, and software development lifecycle.

\section{\faCode}{\Large Professional Experience}
\subsection*{Software Engineer}
TechCorp, San Francisco, CA \hfill June 2021 - Present
Developed and maintained scalable web applications using React and Node.js, improving user engagement by 25%.
Implemented RESTful APIs in Python to integrate third-party services, enhancing functionality and user experience.
Led a team of 4 developers in the creation of a high-traffic e-commerce platform, achieving a 15% reduction in load times.
Conducted code reviews and provided mentorship to junior developers.
Utilized Agile methodologies to manage project timelines and deliverables.

\subsection*{Junior Software Developer}
InnovateTech, San Francisco, CA \hfill January 2019 - May 2021
Contributed to the development of web applications using JavaScript and React, leading to a 20% increase in user satisfaction.
Assisted in the migration of legacy systems to modern architectures, improving system performance and maintainability.
Led a team of two developers on a small-scale project.
Wrote unit and integration tests to ensure code quality.
Participated in daily stand-ups and sprint planning meetings.

\section{\faCheckCircle}{\Large Education}
Bachelor of Science in Computer Science \hfill XYZ University, Boston, MA \hfill Graduated: May 2018
Relevant coursework: Data Structures and Algorithms, Database Systems, Web Development, Software Engineering.
Capstone Project: Developed a machine learning-based recommendation system that increased user engagement by 30%.

\section{\faCheckCircle}{\Large Skills}
Languages: Python, JavaScript, TypeScript, SQL
Frameworks/Libraries: React, Node.js, Express, Django
Tools/Technologies: Git, Docker, Jenkins, PostgreSQL, MongoDB
Methodologies: Agile, Scrum, DevOps
Soft Skills: Problem-solving, Communication, Teamwork, Time management

\section{\faCheckCircle}{\Large Certifications}
Certified JavaScript Developer - CodeAcademy, 2020
Python for Data Science - Coursera, 2021

\section{\faCheckCircle}{\Large Projects}
E-commerce Platform
Developed a full-stack e-commerce application using React, Node.js, and MongoDB, supporting thousands of concurrent users.
Implemented user authentication, product management, and payment processing features.

\section{\faCheckCircle}{\Large References}
Available upon request.

\end{document}
```