```latex
\documentclass[10pt]{resume-template} % Use the custom resume.cls file (see README)
\usepackage{color}
\usepackage{hyperref}
\usepackage[usenames,dvipnames]{color}

\definecolor{linkcolor}{HTML}{3465A0} 

% Define your color choices for headings and text
\definecolor{headingcolor}{HTML}{457B9F} % Heading Color
\definecolor{textcolor}{HTML}{3F51B5} % Text Color
\definecolor{urlcolor}{HTML}{263D6A} 

% Customize page layout and other parameters
\usepackage[left=1.0cm,right=1.0cm,top=1.75cm,bottom=1.75cm]{geometry}
\setlength{\parindent}{0pt} % No indentation for paragraphs

% Define the contact information in a way that allows easy editing
\name{John Doe}
\address{123 Tech Avenue \\ San Francisco, CA 94105 \\ (555) 123-4567 \\ john.doe@email.com \\ \href{https://www.linkedin.com/in/johndoe}{LinkedIn: linkedin.com/in/johndoe} \\ \href{https://github.com/johndoe}{GitHub: github.com/johndoe}}

\makeheadings

% Include a photo if desired (uncomment the line below and comment out the "No Photo" text)
% \photo[0.25]{user_logs/2024_08_25_14_20_50.jpg} % User log directory and file name

\opening

\section{Professional Summary}
Highly skilled Software Engineer with over 3 years of experience in designing, developing, and maintaining web applications. Proven expertise in Python, JavaScript, React, and Node.js. Adept at collaborating with cross-functional teams to deliver high-quality software solutions. Strong background in problem-solving, agile methodologies, and software development lifecycle.

\section{Professional Experience}
% Add more as needed
\begin{entrylist}
\entry
Software Engineer \\
TechCorp, San Francisco, CA \\
June 2021 - Present
Developed and maintained scalable web applications using React and Node.js, improving user engagement by 25%.
Implemented RESTful APIs in Python to integrate third-party services, enhancing functionality and user experience.
Led a team of 4 developers in the creation of a high-traffic e-commerce platform, achieving a 15% reduction in load times.
Conducted code reviews and provided mentorship to junior developers.
Utilized Agile methodologies to manage project timelines and deliverables.
\end{entrylist}

\begin{entrylist}
\entry
Junior Software Developer \\
InnovateTech, San Francisco, CA \\
January 2019 - May 2021
Contributed to the development of web applications using JavaScript and React, leading to a 20% increase in user satisfaction.
Assisted in the migration of legacy systems to modern architectures, improving system performance and maintainability.
Collaborated with UI/UX designers to create intuitive interfaces.
Wrote unit and integration tests to ensure code quality.
Participated in daily stand-ups and sprint planning meetings.
\end{entrylist}

\section{Education}
Bachelor of Science in Computer Science \\
XYZ University, Boston, MA \\
Graduated: May 2018
Relevant coursework: Data Structures and Algorithms, Database Systems, Web Development, Software Engineering.
Capstone Project: Developed a machine learning-based recommendation system that increased user engagement by 30%.

\section{Skills}
Languages: Python, JavaScript, TypeScript, SQL
Frameworks/Libraries: React, Node.js, Express, Django
Tools/Technologies: Git, Docker, Jenkins, PostgreSQL, MongoDB, Elasticsearch

\section{Certifications}
AWS Certified Developer - Associate \\
Google Cloud Professional Cloud Developer (GCP)

\opening

\section{Publications}
"Optimizing Web Application Performance with Machine Learning" \\
"Automated Testing for Modern Web Apps"

\closing
```